\documentclass{article}
% === Document Metadata (Define these BEFORE loading preamble.tex) ===
\newcommand{\docTitle}{Case Study 5: \\The Sovereign Choice Point: \\The Heart of the Discipline}
\newcommand{\docAuthor}{Zack Olinger}
\newcommand{\docVersion}{\csSovereignChoicePointVersion}
\newcommand{\docYear}{2025}

% === Load Shared Config & Version Panel ===
\input{preamble.tex}

\begin{document}

% =============================
% === BEGIN FRONT MATTER ======
% =============================

\pagenumbering{roman}
\pagestyle{frontmatterstyle}

%%%% TTITLE PAGE %%%%

\begin{titlepage}
    \title{\docTitle}
    \author{\docAuthor}
    \date{
        \docVersion \\
        \vspace{1em}
        \today
    }
    \maketitle
    \thispagestyle{empty}

    \begin{abstract}
        \csSovereignChoicePointAbstract
    \end{abstract}

\end{titlepage}

%%%% LICENSE PAGE %%%%

\licensepage

%%%% TABLE OF CONTENTS %%%%

\fancypagestyle{plain}{
    \fancyhf{}
    \fancyfoot[L]{\docVersion}
    \fancyfoot[C]{\href{\licenseURL}{\licenseText}}
      \fancyfoot[R]{Page \thepage\ of \pageref*{LastFrontMatterPage}}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0.4pt}
}


\tableofcontents
\label{LastFrontMatterPage}

% =============================
% === BEGIN MAIN MATTER =======
% =============================

\clearpage
\phantomsection
\pagenumbering{arabic}
\pagestyle{mainmatterstyle}

% === Your content goes here ===

\addcontentsline{toc}{subsection}{Prompt Engineering: Unveiling the Power of Language and Identity}

The video, of which this document is a transcription of, can be found on my YouTube channel and viewed there: \href{https://youtu.be/NivYnGlOLXg}{2023-04-21 - 01: Prompt Engineering: Unveiling the Power of Language and Identity}

\begin{center}
    ---------------------------------------------------
\end{center}

Hey, what's up universe? I made a video back in February talking about how AI is helping me relate to myself and how I see us all as \hyperlink{gloss:prompt}{prompt}\index{Prompt} engineers. And I'm writing about my journey about sharing my experience of self-analysis using language and breaking out sentences of interest through identifying external events or objects that influence me and how I'm using that to understand how that translates into what I'm prompting into my life. And as another way to put it, what I'm manifesting and what I'm contributing and how I'm building my now.

And so this video is a way that I go through using language to help illustrate these ideas and these principles and to kind of lead into what my underlying philosophy is and how I'm approaching myself and the analysis that I'm doing and what's driving my curiosity. And again, I'm writing about this journey on LinkedIn and I'm also sharing the more personal side of this experience on my Instagram account. So if you're at all interested, that's where you can find information related to this particular experience. Thank you for watching and I hope you enjoy the video. Bye.

Hey, what's up universe? It's been a minute and I've been noodling on something for about the past week or two and I thought I'd go ahead and share it with you guys because it's something that is helping me connect with responsibility and manifestation.

So kind of bear with me for a minute because I'm going to go through some words because I share the belief that we speak our life into existence, that words are very powerful. And so I personally like to get into the definition of words and then also the history of words to help me better understand the nature of the word and the intent of the word and the true meaning behind it. It helps me wrap my head around it some more. So with this, with AI, we hear, you may have heard the term like \hyperlink{gloss:prompt}{prompt}\index{Prompt} engineering. And so I'd like to start with that and then I'm going to get into the word relate.

And then I'm going to go through feeling to identity because I wanted to see how I can get my mind to connect with what we feel is to like what we identify with. Because a lot of us say like, I am mad, you know, like I am, and then whatever emotion, emotional state that we're feeling. So we have a strong identity with the feeling. And so I wanted to kind of reverse engineer it in a way. So the way AI is helping me connect with all of this is we'll start with the word \hyperlink{gloss:prompt}{prompt}\index{Prompt}, right? So if you work with any of the art generating AI, Midjourney, Stable Diffusion, whatever, there's a \hyperlink{gloss:prompt}{prompt}\index{Prompt}. You tell it what you want it to create, you \hyperlink{gloss:prompt}{prompt}\index{Prompt} that. ChatGPT, is the same way, you know, it has a \hyperlink{gloss:prompt}{prompt}\index{Prompt}, you type in whatever, it returns something.

So the word \hyperlink{gloss:prompt}{prompt}\index{Prompt}, the definition of that is an event or fact, cause, an event or fact, cause or bring about an action or feeling. So \hyperlink{gloss:prompt}{prompt}\index{Prompt} is a cause. What prompted that? What prompted you to say that? What prompted you to do that? You know, we use this in our own language, so we can relate to that very easily. \hyperlink{gloss:prompt}{Prompt}\index{Prompt} is what's the cause? It's a cause. You feed Midjourney a \hyperlink{gloss:prompt}{prompt}\index{Prompt}, that causes it to create an image. You feed ChatGPT, a \hyperlink{gloss:prompt}{prompt}\index{Prompt}, it causes it to generate an output.

So then the word relate. The word relate, the reason this is so important to me is because of how seemingly simple it is, but how big of an impact it has. To me, this is like the crux of everything. So the word relate, it means to make or show a connection between. Or the second definition is to feel sympathy with or identify with. And so relate is a big piece of our identity. How are we relating to something? Now, relate has an interesting history because the Latin of this word, of relate, has a meaning of bring back or bear back. And so with this, it's about what are we bringing back to \hyperlink{gloss:the_now}{the now}\index{The Now} to create? What are we bringing back from our past into \hyperlink{gloss:the_now}{the now}\index{The Now} to create \hyperlink{gloss:the_now}{the now}\index{The Now}? Because however we're relating to \hyperlink{gloss:the_now}{the now}\index{The Now}, whatever we're bringing back to \hyperlink{gloss:the_now}{the now}\index{The Now}, that's a resource. That's a resource that we're using to create the moment.

And so that goes to our feelings, right? What feelings are we bringing back to now? And if we're talking about our feelings, that means our identity. What identity are we bringing back to now? What resources from our past are we bringing into the present moment to create our now? And so that's why the word relate is such a big piece to me. And I'll get into this about \hyperlink{gloss:prompt}{prompt}\index{Prompt} engineering. So then to start with how feeling goes into our identity, I went through like seven different words.

I started with feeling, right? And the definition of feeling is an emotional state or reaction. Okay, so then I went with emotional state. Define emotion, right? An emotion is a natural instinctive state of mind deriving from one's circumstances, mood, or relationships with others. Relate. Again, what are they bringing back? So it's an instinctive state or a learned state of mind deriving from one's circumstances, moods, or relationships. So it's like deriving from whatever they're bringing back to right now. They call it instinctive, but it's a learned state of mind deriving from. And so it's like, okay, that's what emotion is. Okay, so I am bringing back something that I've learned that's driving emotion. And we know emotion is energy and motion. So define state of mind. And state of mind is basically a person's mood and the effect that mood has on one's person, on that person's thinking and behavior. And so you could say state of mind is somebody's disposition, right? What is their disposition? Then you go from disposition, which is a person's inherent qualities of mind and character. So then you go to character. And that basically, similar words to character are personality. And then from personality, you go to identity.

So you can go from feeling to identity just through the definitions. And so basically what I'm getting at is that if a \hyperlink{gloss:prompt}{prompt}\index{Prompt} is a cause to create something, and how we relate to something describes the resources that we're bringing back into \hyperlink{gloss:the_now}{the now}\index{The Now}, then our \hyperlink{gloss:prompt}{prompt}\index{Prompt} to the universe to create is how we feel. It's our identity.

That helps me connect with my responsibility. And then also how important it is about the state of my being. You know, how do I feel? Because what I feel inside, that's my \hyperlink{gloss:prompt}{prompt}\index{Prompt} to the universe.

What I feel inside of me, what do I identify with? What am I bringing back to right now? All of that influences my energetic state inside of me. And that energetic state is my \hyperlink{gloss:prompt}{prompt}\index{Prompt} to the universe. That's the \hyperlink{gloss:prompt}{prompt}\index{Prompt} that I'm putting out saying, Hey universe, this is what I'm asking for.

And so I just put it that way because if you go to ChatGPT, or you go to Midjourney or whatever, and you put in a \hyperlink{gloss:prompt}{prompt}\index{Prompt} and you're not getting what you want, you're responsible for what you put into that \hyperlink{gloss:prompt}{prompt}\index{Prompt}. And then you're also responsible for changing that \hyperlink{gloss:prompt}{prompt}\index{Prompt} if you want a different outcome.

And so we are all \hyperlink{gloss:prompt}{prompt}\index{Prompt} engineers. It's just that when we're talking about manifestation, it's not what we write out necessarily. It's the feeling. It's the identity. It's the emotion. It's our state of mind. Where are we at? How are we feeling in that moment? That's the \hyperlink{gloss:prompt}{prompt}\index{Prompt}.

Every. Single. Moment. Is a \hyperlink{gloss:prompt}{prompt}\index{Prompt}.

% =============================
% === BEGIN BACK MATTER =======
% =============================

%%%% GLOSSARY %%%%

\newpage
\section*{Glossary of Core Concepts}\label{Glossary of Core Concepts}
\addcontentsline{toc}{section}{Glossary of Core Concepts}


\begin{description}

\input{glossary_sorted_normalized_self_linked.tex}

\end{description}


%%%% INDEX %%%%

\fancypagestyle{plain}{
    \fancyhf{}
    \fancyfoot[L]{\docVersion}
    \fancyfoot[C]{\href{\licenseURL}{\licenseText}}
      \fancyfoot[R]{Page \thepage\ of \pageref*{LastPage}}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0.4pt}
}


\printindex

\end{document}

