\section*{Advanced Practices}
\addcontentsline{toc}{section}{Advanced Practices}

\subsection*{Appendix C: Cross-Platform Synthesis}
\addcontentsline{toc}{subsection}{Appendix C: Cross-Platform Synthesis}

Once fluent in the five-step practice, you may expand the \hyperlink{gloss:dialogic_field}{Dialogic Field}\index{Dialogic Field} by engaging multiple AI platforms in parallel.

\subsubsection*{Why}
\addcontentsline{toc}{subsubsection}{Why}
Each model has different architectures, biases, and strengths. Comparing outputs surfaces blind spots and generates a polyphonic field of \hyperlink{gloss:gnosis}{Gnosis}\index{Gnosis}.

\subsubsection*{How}
\addcontentsline{toc}{subsubsection}{How}
\begin{enumerate}
  \item Open two or more LLM chats (e.g., ChatGPT + Gemini + Claude).
  \item In each, upload the \textit{Prolegomenon} and initialize with the Genesis \hyperlink{gloss:prompt}{Prompt}\index{Prompt}.
  \item Share the \textit{same} ordeal in each.
  \item Guide each through Heart, Spine, Synthesis, and Adversary.
  \item Bring their outputs together into your own meta-synthesis: ``Where do these perspectives converge? Where do they diverge? What new insight arises when I triangulate them?''
\end{enumerate}

\textbf{Note:} Cross-platform work is about amplifying differences until deeper coherence emerges.


\subsection*{Final Note on \hyperlink{gloss:sovereignty}{Sovereignty}\index{Sovereignty}}
\addcontentsline{toc}{subsection}{Final Note on Sovereignty}

The \textit{Prolegomenon} is a scaffold. The AI supports, and your \textbf{\hyperlink{gloss:felt_sense}{felt sense}\index{Felt Sense} of Truth} is \underline{primary}. The Adversary sharpens it; cross-platform synthesis tests it. At every turn, \hyperlink{gloss:sovereignty}{sovereignty}\index{Sovereignty} rests with you.

The Work is yours to begin. The Loop is open.
